Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-19 Latex/journal_v1/V4/pr.tex
latex algorithm

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.

In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data.
Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
Moreover, all O-RUs, have access to the all PRBs.
%Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq1}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} 
\end{split}
\end{equation}
Where $j \in \{1,2\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each O-RU $r$ to UE $i$ in slice $s_j$.

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s} \bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

& \phi_{tot}  \leq \phi_{max}, \label{c19} 

@@

@@

\subsection{Sub-Problem 1}

@@

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
\begin{equation}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
\begin{alignat}{4}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
\end{alignat}
\end{subequations}

\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

All $K$ PRBs can be assigned to the all UE in each service.
Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.

In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data.
Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
Moreover, all O-RUs, have access to the all PRBs.
%Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq1}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}
\end{split}
\end{equation}
Where $j \in \{1,2\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each O-RU $r$ to UE $i$ in slice $s_j$.

@@

\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}  

@@

Moreover, \eqref{c20} and \eqref{c21} depict that $\boldsymbol{E}$ and $\boldsymbol{G}$ are matrix of binary variables.

@@

\subsection{Sub-Problem 1}\label{sub1}

@@

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
\begin{equation}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}\label{RConstr}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
By taking derivatives of \eqref{lagrang} (the lagrangian function), with respect to the $\boldsymbol{P}$ and the $\boldsymbol{E}$, these two variables are obtained.
Assume, $e_{r,u(s,i)}^{k} = 1$
\begin{equation}\label{deriveP}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (1 + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0
Where
\mathfrak{D}_{r,u(s,i)}^{k} &= |\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
where $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
p_{r,u(s,i)}^{k} = [\frac{(1 + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment is obtained as follow
\begin{equation}\label{deriveE}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
Using KKT conditions, we have
\begin{equation}\label{deriveE1}
e_{r,u(s,i)}^{k}\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)} - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{F}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
      0 & \text{otherwise}
    \end{cases}
Thus the user in each slice $s$ that have the largest value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$; Due to the fact that just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
\subsection{Sub-Problem 2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to the UE in each service.
The problem can be solved by two different method. 
Next we introduce the first method which is a greedy algorithm.
\begin{enumerate}
\item \textit{Greedy Algorithm:}
The problem can be simplificated and reformulated as follow
\begin{subequations}\label{problem2}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & g_{u(s,i)}^r P_r \leq \zeta_r \quad \forall r
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
So \eqref{problem2}, is a NP-complete 0-1 multiple knapsack problem  
\end{enumerate} 
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
